---
title: "Dynamic Rebalancing"
author: "John-Craig Borman"
date: "8/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview


## Setup

### Libraries

```{r libs, message=FALSE, warning=FALSE}
# Utility Libraries
library(xts)
library(quantmod)
library(magrittr)
library(dygraphs)
library(lubridate)

# Analytics Libraries
library(PortfolioAnalytics)
library(PerformanceAnalytics)
```

```{r parameters}
tickers <- c("MSFT", "AAPL", "GOOG")
start_years <- 3 # years of historical returns
costs <- c(40, 50, 60)
capital <- 1e7

w_min <- 0.20
w_max <- 0.40
w_incr <- 0.05
```


### Preset Functions

#### Mathematical Formulae

To Do

#### Function Defininitions

```{r functions, echo=TRUE, message=FALSE, warning=FALSE}
# Given a set of portfolio weights and a covariance matrix for those assets
# -> compute the variance (point in time) of that portfolio
variance <- function(weights, cov){
  weights <- as.numeric(weights)
  as.numeric(t(weights) %*% cov %*% weights)
}

# Given the mean (mu) and variance (sigma) of a portfolio/asset
# -> compute the expected utility
expected_utility <- function(mu, sigma){
  as.numeric(log10(1 + mu) - ( sigma / (2 * (1 + mu)^2)))
}

# Given the number of assets (n), a weight range (w_min to w_max) and an increment (w_incr)
# -> compute all possible state spaces of asset weights.
get_state_space <- function(n, w_min, w_max, w_incr){
  require(RcppAlgos)
  vec <- seq(w_min, w_max, w_incr) # Create vector of possible values for weights
  permuteGeneral(v = vec,                # Vector to permute
                 m = n,                  # Choose 'm' weights from the vector of possible weights 'vec'
                 repetition = TRUE,      # Weights can be repeated
                 constraintFun = "sum",  # \ 
                 comparisonFun = "==",   #  } Constrain permutations to sum to 1
                 limitConstraints = 1)   # /
}

# Given an optimal expected utility (opt_EU), an expected utility (EU) and the base capital amount (capital)
# -> compute the certainty equivalent costs - the cost of sub-optimality
CEC <- function(opt_EU, EU, capital){
  as.numeric((exp(opt_EU) - exp(EU)) * capital)
}

# Given the desired weights (w_opt), the current weights (w) and the vector of transaction costs (tc)
# -> compute the transaction costs to switch to the desired weights
TC <- function(w_opt, w, tc){
  w_opt %<>% as.numeric()
  w %<>% as.numeric()
  tc %<>% as.numeric()
  sum(tc * abs(w_opt - w))
}

# Given a time series of returns (rets) and the point in time (date_end)
# -> compute the covariance matrix over the time period (date_end - lookback) to (date_end)
covariance_t <- function(rets, date_end, lookback = years(3)){
  cov(rets[paste0(date_end - lookback, "/", date_end)])
}

# Given a covariance matrix (cov_t)
# -> compute the optimal (minimum variance) portfolio weights
get_opt_weights <- function(cov_t){
  w_opt <- solve(cov_t) %*% rep(1, ncol(cov_t))
  w_opt[,1] / sum(w_opt)
}
```

### Data Retrieval

```{r get_data, message=FALSE, warning=FALSE}
getSymbols(tickers)

pxs <- NULL
rets <- NULL

# Extract adjusted close prices and returns
for(ticker in tickers){
  pxs <- ticker %>% get %>% Ad %>% merge(pxs)
  rets <- ticker %>% get %>% dailyReturn %>% merge(rets)
}

colnames(pxs) <- tickers
colnames(rets) <- tickers

# Preview Data
plot(pxs)
plot(rets)

date_start <- pxs %>% index %>% first + years(start_years)

cov_start <- cov(rets[paste0("/",date_start)])

temp <- rets[paste0(date_start,"/")]

template <- xts(x = matrix(data = 0, nrow = nrow(temp), ncol = 3), order.by = index(temp))
rm(temp)

colnames(template) <- tickers
```

## Portfolio Optimization

### Minimum Variance Portfolio
```{r min_var_portfolio}
opt_w <- get_opt_weights(cov_start)
```

### Dynamic Rebalancing

#### Portfolio Data

```{r holdings_info}
## Holdings Information
weights <- template
investments <- template

weights[1,] <- opt_w
investments[1,] <- weights[1,] * capital

## Cost and Statistics Information
cnames <- c("return", "var", "eu", "opt_var", "opt_eu", "tc", "cec", "costs", "rebalance")
portfolio_data <- xts(x = matrix(data = 0, nrow = nrow(weights), ncol = length(cnames)),
                      order.by = index(weights))
colnames(portfolio_data) <- cnames
```

#### Minimum Cost Weights

```{r min_cost_weights}
## Weight to rebalance
min_cost_weights <- template
```

#### State Space Data

```{r state_space_info}
## Holdings Information
s_weights <- get_state_space(ncol(weights), w_min = w_min, w_max = w_max, w_incr = w_incr) %>% as.data.frame()
s_investments <- matrix(data = 0, nrow = nrow(s_weights), ncol = ncol(s_weights)) %>% as.data.frame()

## Cost and Statistics Information
cnames <- c("return", "var", "eu", "tc", "cec", "costs")
s_portfolio_data <- as.data.frame(matrix(data = 0, nrow = nrow(s_weights), ncol = length(cnames)))

colnames(s_weights) <- tickers
colnames(s_investments) <- tickers
colnames(s_portfolio_data) <- cnames
```

#### Loop through time

```{r main_loop, echo=FALSE, warning=FALSE, include=TRUE}
# Loop through time
for(t1 in 2:(nrow(weights))){
  
  # Calculate daily portfolio movements
  current_date <- index(weights)[t1]
  investments[t1,] <- investments[t1 - 1,] * as.numeric(1 + rets[current_date,])
  weights[t1,] <- investments[t1,] / sum(investments[t1,])
  portfolio_data[t1, "return"] <- (sum(investments[t1,]) / sum(investments[t1 - 1,])) - 1
  
  # Get current covariance matrix and mean return of portfolio
  cov_t <- covariance_t(rets, current_date)
  mean_ret <- mean(portfolio_data$return[2:t1])
  
  # Add Information to Portfolio Data
  portfolio_data$var[t1] <- variance(weights[t1,], cov_t)
  portfolio_data$eu[t1] <- expected_utility(mean_ret, portfolio_data$var[t1])
  
  # Get Current Optimal Portfolio Information
  opt_w <- get_opt_weights(cov_t)
  opt_var <- variance(opt_w, cov_t)
  opt_eu <- expected_utility(mu = mean_ret, sigma = opt_var)
  
  # Add Information to Portfolio Data
  portfolio_data$opt_var[t1] <- opt_var
  portfolio_data$opt_eu[t1] <- opt_eu
  
  # Add information to state space
  s_portfolio_data$return <- as.numeric(portfolio_data[t1, "return"])
  s_investments <- s_weights * sum(investments[t1,])

  # Loop through each possible set of weights (each possible state 's' in the set of states 'S')
  for(s in 1:nrow(s_portfolio_data)){
    
    # Calculate variance and E[U] for state space 's'
    s_portfolio_data$var[s] <- variance(weights = s_weights[s,], cov = cov_t)
    s_portfolio_data$eu[s] <- expected_utility(mu = mean_ret, sigma = s_portfolio_data$var[s])
    
    # Calculate costs to switch to state space 's'
    s_portfolio_data$tc[s] <- TC(w_opt = weights[t1,], w = s_weights[s,], tc = costs)
    s_portfolio_data$cec[s] <- CEC(opt_EU = opt_eu, 
                                   EU = s_portfolio_data$eu[s], 
                                   capital = sum(investments[t1,]))
  }
  
  # Calculate total costs of switching to each state
  s_portfolio_data$costs <- rowSums(s_portfolio_data[, c("tc", "cec")])
  
  # Identify the minimum cost index and weights
  min_cost_idx <- which.min(s_portfolio_data$costs)
  min_cost_weights[t1,] <- s_weights[min_cost_idx,] %>% as.numeric()
  
  # Add minimum cost rebalancing to portfolio data
  portfolio_data[t1, c("tc", "cec")] <- s_portfolio_data[min_cost_idx, c("tc", "cec")] %>% as.numeric()
  
  # If a weight exceeds the maximum or minimum individual asset weight (w_max or w_min)
  # -> rebalance the portfolio
  if (any(weights[t1,] > w_max) || any(weights[t1,] < w_min)){
    
    portfolio_data[t1, "rebalance"] <- 1
    
    # The minimum cost weight becomes the new weight
    weights[t1,] <- min_cost_weights[t1,]  
    
     # Adjust the asset investments accordingly
    investments[t1,] <- weights[t1,] * sum(investments[t1,])
    
    # Subtract realized transaction costs from portfolio return
    portfolio_data[t1, "return"] <- portfolio_data[t1, "return"] - (portfolio_data[t1, "tc"] / 100)
  
  }
}
```


## Analysis of Results

### Extract Data

Collect Returns

```{r collect_returns}
returns <- portfolio_data$return
rebalances <- portfolio_data$rebalance %>% subset( (.) %>% equals(1))
```

### Portfolio Overview

```{r overview, echo=FALSE, fig.keep='last'}
chart.CumReturns(returns, main = "Cumulative Return")
addEventLines(events = rebalances, lwd = 0.3)
addSeries(returns, main = "Daily Return")
addEventLines(events = rebalances, lwd = 0.3)
addSeries(weights, main = "Weights")
addEventLines(events = rebalances, lwd = 0.3)
```

#### Returns Analysis

##### Stats

```{r return_stats}
kurtosis(returns)
skewness(returns)
SkewnessKurtosisRatio(returns)
```

##### Distribution

```{r distributions, echo=FALSE}
chart.ECDF(returns)
chart.QQPlot(returns, distribution = "norm")
hist(returns)
```

#### Portfolio Performance Tables

```{r perf_tables, echo=FALSE}
table.Stats(returns)
```

#### Portfolio Performance Charts

```{r perf_charts, echo=FALSE}
charts.PerformanceSummary(returns, main = "Dynamic Rebalancing")
charts.RollingPerformance(returns, main = "Dynamic Rebalancing")
chart.Boxplot(returns)

layout(rbind(c(1,2), c(3,4)))
chart.Histogram(returns, main = "Plain", methods = NULL)
chart.Histogram(returns, main = "Density", breaks=40, methods = c("add.density", "add.normal"))
chart.Histogram(returns, main = "Skew and Kurt", methods = c("add.centered", "add.rug"))
#chart.Histogram(returns, main = "Risk Measures", methods = c("add.risk"))
```

#### Portfolio Risk Tables

```{r risk, echo=FALSE}
table.DownsideRisk(returns)
table.DownsideRiskRatio(returns)
table.Drawdowns(returns)
```











